Type Visualization for R

### 2020-06-18 paper/main.tex
paper: Finish intro

To analyze one aspect of programming languages, we built {\sc TypeVis},
an interactive visualization of run-time types for the language R.
{\sc TypeVis} builds on a dataset of concrete execution traces
over the most widely used libraries in the R ecosystem.
Our visualization supports three broad tasks:
filtering the dataset down to a digestible subset,
understanding the types of function arguments and returns,
and comparing across different functions.
\todo{Explain the components of the design and how they support these tasks.}

These tasks can assist language designers during different
phases of development.
For example, exploratory data analysis can weed out designs that
are incompatible with existing programs.
\todo{Give specific motivation, i.e. gradual typing.}

Supplemental material, including the data and source code of
{\sc TypeVis}, is freely available: \todo{Fill with archival link}

@@

These goals can be classified using an abstract task analysis framework.
In table~\ref{tab:tasks}, we use Munzner's mid-level and low-level
abstract task taxonomy. \todo{Cite Munzner}

@@

\subsection{Package and Function Filtering}

>>>>

To analyze one aspect of programming languages, we built {\sc TypeVis},
an interactive visualization of run-time types for the language R.
{\sc TypeVis} builds on a dataset of concrete execution traces
over the most widely used libraries in the R ecosystem.
Our visualization supports three broad tasks:
filtering the dataset down to a digestible subset,
understanding the types of function arguments and returns,
and comparing across different functions.
For filtering, {\sc TypeVis} uses the treemap idiom
to convey the relative scale of different packages.
Once a specific function is selected,
type signatures are represented as flows over types
where the width of the flow is proportional to frequency.
These flows can be readily compared within the same function,
or across different functions.

Tasks enabled by {\sc TypeVis} can assist language designers
during many phases of development.
For example, exploratory data analysis can weed out designs that
are incompatible with existing programs.
In particular, the visualization is built to answer questions
relevant to gradual type system development.
Supplemental material, including the data and source code of
{\sc TypeVis}, is freely available: \todo{Fill with archival link}

@@

These goals can be classified using an abstract task analysis framework.
See table~\ref{tab:tasks} for a categorization of these domain tasks
into Munzner's mid-level and low-level abstract task taxonomy. \todo{Cite Munzner}

@@

\subsection{Function Filtering}
